### 2016-08-17 gruntz.tex
SYMPY_DEBUG needs to be set specifically to True

In this example the result ($2+{1\over x}$) still depends on $x$, so the above procedure is
repeated until just a value independent of $x$ is obtained. This is the final
limit. In the above case the limit is $2$, as can be
verified by SymPy:

>>>>

In this example the result ($2+{1\over x}$) still depends on $x$, so the above procedure is
repeated until just a value independent of $x$ is obtained. This is the final
limit. In the above case the limit is $2$, as can be
verified by SymPy\footnote{To see intermediate steps, discussed above, interested
readers can switch on debugging output by setting
the environment variable \texttt{SYMPY\_DEBUG=True}, before importing anything from
the SymPy namespace.}:
